---
title: "AncCond Practice"
author: "Nathan"
date: "11/3/2021"
output: pdf_document
vignette: > 
  %\VignetteIndexEntry{figures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Documents/GitHub/Ancestral-Condition-Test/cleaned")
```

## Introduction

First let's load in an example phylogeny.

```{r}
library(phytools)
tree <- read.tree(file = 'Data/whales.tre')
plot(tree, cex = 0.25)
```
That's a lot of whales!

Wonder how big they are, let's import thier weights.

```{r}
load(file = 'Data/exampleSizeData.RData')
length(sizedata)
length(tree$tip.label)
```
We dont have size data for all of the species!

lets fix that

```{r}
tree <- keep.tip(tree, names(sizedata))
plot(tree, cex = 0.25)
```
The sizes are our continious trait.

Lets perform an ancestral state estimation on the size data of extant whales.

```{r}
contMap(tree,sizedata, fsize = 0.5)
# , ftype = 'off', legend = F, lims = c(.24,2), plot = F)
# n<-length(smp$cols)
# smp$cols[1:n]<-rainbow(n, end = 4/6)
# plot(smp, legend = F,ftype = 'off')
```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
